---
title: "Inclass Assignment (6)"
author: "Charles Miller"
date: "3/2/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Run this line first
```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
```

Q1. Update the author name and date in YAML part above. 

Q2. A line of code to import the `student.csv` file from your `Desktop` folder and create `department` data for this assignment
```{r}
department <- read.csv("C:/Users/cmill214/Desktop/student.csv")
```

Q3. A line of code to return column names of `department` data 
```{r}
colnames(department)
```

Q4. Two lines of code to divide `height` column of `department` data into `height_a` and `height_b`
```{r}
department %>%
  separate(height, into = c("height_a", "height_b"))

```

Q5. Two lines of code to combine `sex` and `race` column into `demo` column (with an underscore)
```{r}
department %>%
  unite(demo, sex, race)

```

Q6. Two lines of code to combine `sex` and `race` column into `demo` column (WITHOUT an underscore)
```{r}

department %>%
  unite(demo, sex, race, sep = "")

```

#run this code to make a `stock` data
```{r}
stock <- tibble(
  time   = c(2015, 2015, 2015, 2015, 2016, 2016, 2016),
  division    = c(   1,    2,    3,    4,    2,    3,    4),
  profit = c(23, 452, 888,   NA, 3234, 279, NA)
)
```

Q7. How many implicit and explicit NA values does `stock` data have?
```{r}
View(stock)
# implicit NA = 1
# explicit NA = 2
```

Q8. Two lines of code to change implicit NA values into explicit ones using `pivot_wider()` (*tip: `time` and `profit` column)
```{r}
stock %>%
  pivot_wider(names_from = time, values_from = profit)

```

Q9. Two lines of code to change implicit NA values to explicit ones using `complete()` (*tip: `time` and `division` column)
```{r}
stock %>%
  complete(time, division)

```

Q10. Three lines of code to fill in the NA value with the most recent non-missing value using `fill()`
```{r}
stock %>%
  complete(time, division)%>%
  fill(profit)

```
