---
title: "Inclass Assignment (7)"
author: "John Doe"
date: "7/07/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Handling Text with `stringr` Package

# Run these two lines first
```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
if (!require('stringr')) install.packages('stringr'); library('stringr') 
```

Q1. Update the author name and date in YAML part above. 

Q2. A line of code to create a variable `yolo` that stores a string of "You only live once" 
```{r}

yolo <- "You only live once"

```

Q3. A line of code to check data type of `yolo` variable
```{r}

typeof(yolo)

```

Q4. A line of code to return length of `yolo` variable
```{r}

str_length(yolo)

```

Q5. Add a correct parameter and value to return "You, only, live, once" (*note there are commas)
```{r}

str_c("You", "only", "live", "once", sep = ",")

```

Q6. Add a correct parameter and value to return "Youonlyliveonce" (*note there is no blank)
```{r}

paste("You", "only", "live", "once", sep = "")

```

Q7. Add a correct parameter and value to return "You_only_live_once" (*note there are underscores)
```{r}

paste("You", "only", "live", "once", sep = "_")

```

Q8. A line of code to return "You" "onl" "liv" "onc" using `yolo_con` variable and `str_sub()` function 
```{r}
yolo_con <- c("You", "only", "live", "once")
str_sub(yolo_con,1,3)

```

Q9. A line of code that returns "live" "once" "only" "You" using `yolo_con` variable (*alphabetical order sorting)
```{r}

yolo_con <- c("You", "only", "live", "once")
str_sort(yolo_con)

```

Q10. A line of code that returns "You", "only", "live", "once" as "Youonlyliveonce" using `paste0()` function
```{r}

paste0("You","only","live","once")

```