---
title: "Inclass Assignment"
author: "John Doe"
date: "9/03/1958"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Handling Date & Time w/ `lubridate` Package

# Run these lines first
```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse')
if (!require('lubridate')) install.packages('lubridate'); library('lubridate')
if (!require('nycflights13')) install.packages('nycflights13'); library('nycflights13')
```

Q1. 
Update the author name and date in YAML part above

Q2. 
A line of code to output current year, date, and time
```{r}

now()

```

Q3. 
A line of code to parse date from "March 23rd 2022"
```{r}

mdy("March 23rd 2022")

```

Q4. 
A line of code to parse date from "23rd March 2022 05:23:34" 
```{r}

dmy_hms("23rd March 2022 05:23:34")

```

Q5. 
A line of code to return `flights` data column names
```{r}

colnames(flights)

```

Q6. 
Three lines of code to select `year`, `month`, `day`, `hour`, `minute` columns from `flights` data and then 
create a new column called `reservation` using `make_datetime()` function
```{r}
flights %>%
  select(year, month, day, hour, minute) %>%
  mutate(reservation = make_datetime(year, month, day, hour, minute))

```

Q7. 
Using three lines of code for Q6, please add two additional codes to visualize 
the count of `reservation` column using `ggplot()` and `geom_freqploly(binwidth = 86400)` functions (*1 day = 86400 seconds)
```{r}
flights %>%
  select(year, month, day, hour, minute) %>%
  mutate(reservation = make_datetime(year, month, day, hour, minute)) %>%
  ggplot(aes(reservation)) +
  geom_freqpoly(binwidth = 86400)

```

Q8. 
Using three lines of code for Q6, please add three additional codes to make 
a new column called `w_reservation` that contains days of the week for `reservation` column and its label
and then `a bar plot` of `w_reservation` applying `ggplot()` and `geom_bar()` functions
```{r}
flights %>%
  select(year, month, day, hour, minute) %>%
  mutate(reservation = make_datetime(year, month, day, hour, minute)) %>%
  mutate(w_reservation = wday(reservation, label = TRUE)) %>%
  ggplot(aes(w_reservation)) +
  geom_bar()

```

Q9. Bill Gates was born in Seattle on October 28, 1955. What day of the week was he born? Provide two lines of code for this question and exact answer.    
```{r}
birthday <- mdy("October 28 1955")
wday(birthday, label = TRUE, abbr = FALSE)
Friday
```

Q10. What is the time difference (as days) between today and Bill Gates birthday? Provide a line of code for this question and exact answer.  
```{r}
today() - mdy("October 28 1955")
24253
```
