---
title: "Inclass Assignment"
author: "Charles Miller"
date: "3/30/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# if statement and function 

Q1. 
Update the author name and date in YAML part above. 

Q2. 
Lines of code to describe the basic syntax of `if` statement (use 'condition' and 'expression')
```{r}
if(condition1){
  expression1
}

```

Q3. 
Bill's current height is 6.2. Create an if statement to print "Bill is taller than 5.8" if Bill's height is greater than 5.8. 
```{r}

Bill <- 6.2

if(Bill > 5.8){
  print("Bill is taller than 5.8")
}

```

Q4. 
The current number of student is 5. Create an `if statement` to print "number of student is not even" if the current number of student (`nstudent`) is an odd number, using `%%` operator to set a remainder of `nstudent` divided by 2 is NOT equal to zero. 
```{r}

nstudent <- 5
if(nstudent %% 2 != 0){
  print("number of student is not even")
}

```

Q5. 
Lines of code to describe the basic syntax of `else` statement (use 'condition' and 'expression')
```{r}
if(condition1){
  expression1
} else {
  expression2
}
```

Q6. 
Using an `else statement`, Jane wants to print out "Profit is excellent!" if `profit` is greater than 100, while "Profit is not good" if `profit` is equal or less than 100. Please help her with writing a proper else statement.  
```{r}
profit <- 50
if(profit > 100){
  print("Profit is excellent!")
} else {
  print("Profit is not good")
}
```

Q7. 
Lines of code to describe the basic syntax of `else if` statement (use `condition`, `expression`, etc. as parameter names)
```{r}
if(condition1){
  expression1
} else if(condition2){
  expression2
} else {
  condition3
}

```

Q8. 
Using an `else if statement`, James wants to print out "Profit is excellent!" if `profit` is equal to 100. At the same time, he wants to print out "Profit is good" if `profit` is equal to 50. Otherwise he wants to print out "Profit is not what I expected". Please help him with writing a proper else if statement. 
```{r}
if(profit == 100){
  print("Profit is excellent!")
} else if(profit == 50){
  print("Profit is good")
} else {
  print("Profit is not what I expected")
}


```

Q9. 
Create a function with a single parameter `h` that includes an if statement where a print function ("The input is 10") works if `h` is equal to 10. And then assign the function to `findten`. 
```{r}
findten <- function(h){
  if(h == 10)
    print("The input is 10")
}
findten(10)
```

Q10. 
Create a function with a single parameter `department` that includes two print functions. The first print function shows mean of `department` and the second print function outputs maximum value of `department`. And the assign the function to `printboth`.  
```{r}
printboth <- function(department){
  print(mean(department))
  print(max(department))
}
department <- c(45, 50, 55)
printboth(department)
```