---
title: "Inclass Assignment (2)"
author: "Charles Miller" # your name
date: "1/26/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Data visualization using ggplot2 package 

```{r, message=FALSE}
install.packages("ggplot2") 
library("ggplot2") 
```

Q1. Replace the current author name with your name in YAML part above. 

Q2. What are three components for a single plot of ggplot2? 
```{r}
# component 1: data
# component 2: mapping aes (x,y)
# component 3: color
```

Q3. A line of code that shows a help page for ggplot2
```{r}
help("ggplot2")
```

## 2) Data preview

Q4. A line of code that shows `midwest` data as a table
```{r}
View(midwest)
```

Q5. A line of code that shows `midwest` data summary
```{r}
summary(midwest)
```

Q6. A line of code that shows `midwest` data column name
```{r}
colnames(midwest)
```

Q7 A line of code that shows unique values in `state` column of `midwest` data
```{r}
unique(midwest$state)
```


Q8. A line of code that assigns `popamerindian` column as `x` position and `popasian` column as `y` position of `midwest` data to a variable `myplot` using `ggplot` function
```{r, fig.height=3, fig.width=3}
myplot <- ggplot(data = midwest, aes(x = "popamerindian", y = "popasion"))
```

Q9. Two lines of code that create a scatter plot of a variable `myplot` that you have made in Q8 
```{r,  fig.height=3, fig.width=3}
myplot +
  geom_point()
```

Q10. Three lines of code that create subplots (three rows) by `state` column using two lines of code for Q9.

```{r, fig.height=5, fig.width=5}
myplot +
  geom_point() +
  facet_wrap(~ state,nrow = 3)
```

#### *End of document*