---
title: "Inclass Assignment (3)"
author: "Charles Miller"
date: "2/2/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

```{r, include=FALSE}
if (!require('ggplot2')) install.packages('ggplot2'); library('ggplot2') 
```

# Data visualization using ggplot2 package (2)

***
### If you want to make a presentation to review this assignment next Monday, please reach me at jlim13@uncc.edu

### If you don't know the answer, leave it blank. If you are caught cheating, you will be given minus 50 points.   
***

Q1. Replace the author name with your name in YAML part above. 

Q2. The first method for a quick overview of `msleep` data 
```{r}

summary(msleep)

```

Q3. The second method for a quick overview of `msleep` data 
```{r}

str(msleep)
```

Q4. A line of code that returns unique values in `vore` column of `msleep`
```{r}

unique(msleep$vore)

```

Q5. A line of code that assigns `vore` column as `x` position of `msleep` data to a variable `msleep_plot` using `ggplot` function
```{r}
msleep_plot <- ggplot(data = msleep, aes(x = vore))

```

Q6. Two lines of code that will return a bar plot of the `msleep_plot` variable 
```{r, out.width='50%'}
msleep_plot +
  geom_bar()

```

Q7. Five lines of code that will return a bar plot of the `msleep_plot` variable with a title `Plot of count by vore`. X-axis is labeled as `vore` and y-axis as `count`.   
```{r, out.width='50%'}
msleep_plot +
  geom_bar() +
  ggtitle("Plot of count by vore") +
  xlab("vore") +
  ylab("count")
```

Q8. A line of code that assigns `vore` column as `x` position, proportion as "y" column of `msleep` data to a variable `msleep_prop'
```{r} 
msleep_prop <- ggplot(data = msleep, aes(x = vore, y = ..prop.., group = 1))

```

Q9. Five lines of code that will return a bar plot of the `msleep_prop` variable with a title `Plot of proportion by vore`. X-axis is labeled as `vore` and y-axis as `proportion`. 
```{r}
msleep_prop +
  geom_bar() +
  ggtitle("Plot of proportion by vore") +
  xlab("vore") +
  ylab("proportion")

```

Q10. Two lines of code that will directly create a simple stacked bar plot that shows the count by `vore` column of `msleep` data with filling color by `conservation` column
```{r}
ggplot(data = msleep, aes(x = vore, fill = conservation)) +
  geom_bar()
  

```

### *End of document*