---
title: "Inclass Assignment (4)"
author: "Charles Miller"
date: "2/9/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Data manipulation using `dplyr` package (1)
# If you don't know the answer, leave it blank. 
# If you are caught cheating, you will be given minus 50 points.  

# Run this chunk first
```{r}
if (!require('dplyr')) install.packages('dplyr'); library('dplyr') 
```

Q1. Update the author name and date in YAML part above. 

Q2. A line of code that returns the first four rows of `starwars` dataset
```{r}
head(starwars, 4)
```

Q3. A line of code that returns the last six rows of `starwars` dataset
```{r}
tail(starwars, 6)
```

Q4. A line of code that returns unique values in `eye_color` column of `starwars`
```{r}
unique(starwars$eye_color) 
```

Q5. Explain the meaning of the following two abbreviations for R data type 
```{r}
# `int` = integer
# `fctr` = factor
```

Q6. What is the role of `arrange()` function of the `dplyr` package? Use a hashtag when you add an answer.
```{r}
# arrange() = reorder rows
```

Q7. What is the role of `mutate()` function of the `dplyr` package? Use a hashtag when you add an answer.
```{r}
# mutate() = create new functions
```

Q8. A line of code that filters the rows by `height` values (167 or 96) of `starwars` data
```{r}
filter(starwars, height == 167 | height == 96)
```

Q9. A line of code that filters the rows by `height` values (167 or 96) of `starwars` data, using `%in%` operator
```{r}
filter(starwars, height %in% c(167, 96))
```

Q10. What is the hair color of the row in which `mass` is `82` and `birth_year` is `92`?
```{r}
filter(starwars, mass == 82, birth_year == 92)
white hair
```

### *End of document*