---
title: "HW(1) Project"
author: "Charles Miller"
date: "2/6/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Run this code first
```{r, include=FALSE}
if (!require('ggplot2')) install.packages('ggplot2'); library('ggplot2') 
```


# Q1. Replace the author name with your name in YAML part above. 

# Q2. Find `Position Adjustments` section from the cheat sheet and apply one of its methods with your comment
 
```{r}
q2 <- ggplot(mpg, aes(fl, fill = drv)) # creating my variable `q2` # Do not modify this line
```

```{r, out.width='50%'}
q2 + geom_bar(position = "jitter")
```

# Q3. Find `ONE VARIABLE continuous` section and apply one of its methods with your comment 
```{r}
q3 <- ggplot(mpg, aes(hwy)) # creating my variable `q3` # Do not modify this line
```

```{r, out.width='50%'}
q3 + geom_freqpoly()
```

# Q4. Find `COLOR AND FILL SCALES (CONTINUOUS)` section and apply one of its methods with your comment 
```{r}
q4 <- q3 + geom_dotplot(aes(fill = ..x..)) # Creating my variable `q4` # Do not modify this line
```

```{r, out.width='50%'}
q4 + scale_fill_gradientn(colors = topo.colors(6))
```

# Q5. Find `both discrete` section and apply one of its methods with your comment 
```{r}
q5 <- ggplot(mpg, aes(cyl, hwy)) # Creating my variable `q5` # Do not modify this line
```

```{r, out.width='50%'}
q5 + geom_count()
```

### *End of document*
